In-silico molecular enrichment and clearance of the human intracranial space

### 2025-02-25 paper/main.tex
update Fig1 caption and references

\subsection*{In-silico predictions of intracranial molecular enrichment and clearance after intrathecal injection}
\begin{figure}
    \centering
    \includegraphics[width=0.98\textwidth]{figures/figure1.png}
     \caption{
     \textbf{Our in-silico model predicts tracer transport in PVS, SAS and parenchyma following intrathecal injection.}\\
     A) Illustration of the spatial domains of the model: CSF-filled space (ventricles and SAS) $\Omega_{\rm CSF}$, parenchyma $\Omega_{\rm PAR}$ and the PVS surrounding arteries $\Lambda_{\rm artery}$ and the veins $\Lambda_{\rm vein}$ and their interfaces and boundaries (see Methods); 
     B) 3D rendering of the actual geometry used in this study parenchyma, CSF (clipped, blue), arterial network (red), venous network (blue)); 
     C) illustration of the modelled clinical tracer injection procedure; 
     D) simulated tracer concentration after 1, 6, 12, and 24 hours (opacity increases linearly from 0 to $2\,$mol/l); 
     E) sagittal, coronal and axial view of computed tracer concentrations over T1-image after 1, 6, 12 and 24\,h (low concentrations transparent, pial surface in pink, arachnoid membrane in cyan, and arteries in dark red); 
     F) total amount of tracer in each cranial compartment over the first 24\,h; 
     G) average tracer concentration in each compartment over the first 24\,h. }
     \label{fig:results1}
\end{figure}
Using previously published multi-modal magnetic resonance imaging
(MRI) data~\cite{hodneland2019new, deistung2009tof,
  schweser2012quantitative, reichenbach2012future,
  deistung2017overview}, we construct a multiscale computational
representation of the human intracranial compartments consisting of
the CSF spaces and brain parenchyma as three-dimensional (3D) domains
and with the PVSs surrounding major surface arteries and veins as
embedded networks of topologically one-dimensional (1D) curves
(\Cref{fig:results1}A--B). We consider a solute concentration field,
varying in space and time, in the 3D domains and in the PVS networks,
and assume that the solute can cross between these compartments
through semi-permeable membranes. As the drivers and modes of
intracranial transport are under substantial
debate\cite{smith2019going, proulx2021cerebrospinal,
  bohr2022glymphatic, hladky2022glymphatic, betsholtz2024advances},
our first target is to establish a baseline model accounting for a
reasonably conservative set of mechanisms and their integrated effect
over a timescale of several minutes to a few days. To this end, we
assume that the solute will (i) diffuse within all compartments, with
diffusivity depending on the effective properties of the relevant
medium\cite{sykova2008diffusion}; (ii) experience significant
dispersive effects due to the pulsatile flow of CSF induced by the
cardiac and respiratory cycles\cite{vinje2019respiratory,
  sharp2019dispersion, ray2021quantitative, troyetsky2021dispersion};
and (iii) be convected by a (small) net flow of CSF resulting from
production in the choroid plexus with CSF efflux across the upper
convexity\cite{hornkjol2022csf} and from the peristaltic pumping
effect of pulse wave pulsations in surface periarterial
spaces~\cite{mestre2018flow, gjerde2023directional}. Mathematically, this model is represented by a
mixed-dimensional system of coupled time-dependent partial
differential equations\cite{masri2024modelling}, which we solve
numerically with high accuracy using a mass-conserving finite element
scheme and the FEniCS finite element software\cite{alnaes2015fenics,
  kuchta2020assembly} (see Methods). The computational framework and
associated software are all openly available~\cite{ZENODO}.

Simulating a glymphatic MRI protocol~\cite{ringstad2017glymphatic,
  ringstad2018brain, eide2024functional}(\Cref{fig:results1}C), we then predict the
spreading of $0.5$ mmol intrathecally injected Gadobutrol after its
appearance at the craniocervical junction
(\Cref{fig:results1}D--E). After one hour, the in-silico
tracer moves upwards in the SAS frontally of the brainstem, and
quickly reaches the supratentorial regions. Here, it spreads both
posterior through the quadrigeminal cistern and the longitudinal
fissure, and anteriorly through the outer SAS, reaching the top of the
cerebral cortex after around 12 hours. After 24 hours, the tracer
covers most of the brain surface (with the exception of some posterior
regions) and has penetrated substantially into the parenchymal
tissue. This pattern is reflected in the mean tracer concentrations in
each compartment, where the CSF space reaches its peak of
$1.4\,$mmol/l after 2 hours, followed by the arterial PVS
concentration peak ($2.9\,$mmol/l after 4 hours)
(\Cref{fig:results1}G). While the mean concentrations in these
compartments drop soon after peaking, the parenchymal tissue
slowly enriches with tracer over the first 24 hours, with a final
value of $0.3$ mmol/l. Overall, about 40\% of the total amount of
tracer remains in the cranium 24 hours post-injection, with the largest
share in the CSF (53\%), followed by the parenchyma (35\%), the
venous PVS (8\%) and the arterial PVS
(5\%) (\Cref{fig:results1}H).

@@

Our periarterial network extends from the internal carotid arteries
and basilar artery through up to 18 bifurcations to reach upstream
network ends located within the SAS or up to 6 mm inside the
parenchyma (\Cref{fig:results1}A--C, \Cref{fig:pvs_a}A) and includes
major surface arteries of radius 0.5--1.4 mm. Imposing the pressure
field induced by CSF production at the periarterial network ends
induces slow steady CSF flow of variable direction in these PVSs, with
an average velocity of 0.08 \textmu m/s (antegrade) and a maximum
velocity of 0.55 \textmu m/s (\Cref{fig:pvs_a}B). On the other hand,
traveling waves of arterial wall motion (\Cref{fig:pvs_a}C), such as
the pulse wave or other vasomotion~\cite{vanveluw2020vasomotion,
  munting2023spontaneous, bojarskaite2023sleep,
  broggini2024long,hauglund2025norepinephrine}, also induce net
directional flow in the PVS~\cite{kedarasetti2020arterial,
  kedarasetti2020functional, coenen2021lubrication,
  gjerde2023directional, nozaleda2024arterial} -- of magnitude and
direction depending on the amplitude, frequency, and length of the
waves and the characteristics of the perivascular
network~\cite{gjerde2023directional}. Applying a semi-analytic model
of the net flow induced by peristalsis in perivascular
networks~\cite{gjerde2023directional} (see Methods), we estimate that
the cardiac pulse wave alone, travelling at a frequency of 1 Hz with a
wavelength of 2.0 m and a 1\% wall displacement~\cite{jung2021novel},
will induce mainly antegrade PVS flow with an average net velocity of
0.92 \textmu m/s while reaching up to 7.31 \textmu m/s near larger,
ventral vessels such as the MCA (\Cref{fig:pvs_a}D,E). The same theory
predicts that strong ultraslow vasomotions, if travelling antegrade at
0.1Hz with a wavelength of 0.02 m and a 10\%
displacement~\cite{broggini2024long}, will induce both retrograde and
antegrade net PVS flow with an average velocity of 13.05 \textmu m/s
and maximum velocity 54.44 \textmu m/s (\Cref{fig:pvs_a}D,F).

@@

To represent surface networks of periarterial and perivenous spaces,
we use Kiminaro~\cite{william_silversmith_2021_5539913} to separately
skeletonize time-of-flight angiography (ToF) and quantitative
susceptibility mapping (QSM) images from the same human
subject~\cite{hodneland2019new}. This technique yields networks of
one-dimensional curves, each curve $\Lambda^i$ indicating the
centerline of a blood vessel segment and labeled with its lumen radius
$R_1^i$ (\Cref{fig:results1}C, \Cref{fig:pvs_a}A). We also assign an
outer radius $R_2^i > R_1^i$ to each segment $i$, form the annular
cylinder ensheathing $\Lambda^i$ and define the union of these as the
PVS. The periarterial network graph consists of $12\,708$ edges
connected at $12\,562$ inner nodes and with $147$ end nodes, and the
associated domain is denoted by $\Lambda_a$. We identify three of the
end nodes -- corresponding to the two internal carotid arteries (ICAs)
and the basilar artery (BA) -- as root nodes, and designate the other
ends as leaf nodes. The resulting perivenous network graph consists of
$24\,829$ edges connected at $23\,881$ inner nodes and with $949$ end nodes, and the associated domain is denoted by $\Lambda_v$. Finally, we label the outer surface of the PVSs associated with $\Lambda_a$ and $\Lambda_v$, by $\Gamma_a$ and $\Gamma_v$ respectively.

@@

We model diffusion, convection, and exchange of a molecular solute in
the PVS networks $\Lambda_a$ and $\Lambda_v$, in the CSF spaces
$\Omega_{\rm CSF}$ and in the brain parenchyma $\Omega_{\rm PAR}$ via
a mixed-dimensional transport model~\cite{masri2024modelling,laurino2019derivation} over a
timescale of minutes to hours (\Cref{fig:results1}A--C,
\Cref{fig:csf}A--C). Specifically, for $t > 0$, we solve for a
concentration $c = c(x, t)$ in the 3D intracranial compartments ($x
\in \Omega_{\rm CSF}, x \in \Omega_{\rm PAR}$) and for a cross-section
averaged concentration $\hat{c} = \hat{c}(s, t)$ in the periarterial
and perivenous networks ($s \in \Lambda_a, s \in \Lambda_v$) such that
the following equations hold:
\begin{subequations}
\begin{alignat}{2}
  \partial_t (\phi c) - \nabla \cdot (D \nabla (\phi c) ) + \nabla \cdot (\bm u c ) + \xi (\overline{c} - \hat c ) \delta_\Gamma & = 0 && \quad \quad \mathrm{in} \quad \Omega_{\rm CSF}, \Omega_{\rm{PAR}},
  \label{eq:multi_transport_3d}
  \\ 
  \partial_t (A  \hat c) - \partial_s(\hat D A \partial_s ( \hat c)) +\partial_s(A \hat u \hat c )  +  \xi P (\hat c - \overline{c})  &= 0 && \quad \quad \mathrm{in} \quad  \Lambda_a, \Lambda_v .
  \label{eq:multi_transport_1d}
 \end{alignat}%
\label{eq:multi_transport}%
\end{subequations}%
In~\eqref{eq:multi_transport}, $0 < \phi \leqslant 1$ is the fluid
volume fraction, $D$ and $\hat{D}$ are effective diffusion
coefficients, and $\bm u$ and $\hat{u}$ are fluid (CSF/ISF)
velocities, all defined in the respective compartments; $P = 2 \pi
R_2$ is the perimeter and $A = \pi (R_2^2 - R_1^2)$ the area of the
PVS cross-sections, $\delta_{\Gamma}$ is a Dirac term concentrated on
the interfaces $\Gamma_a, \Gamma_v$, the overlined $\overline{c}$
denotes the average of $c$ over cross-sections of $\Gamma_a,
\Gamma_v$, and $\xi$ is a permeability allowing for transfer/exchange
over the interfaces $\Gamma_a, \Gamma_v$ between the periarterial and
perivenous networks and their surroundings.  Moreover, we model the
membrane between the parenchyma and the CSF spaces as a semi-permeable
membrane with permeability coefficient $\beta_{\rm pia}$. For a
complete description of this mathematical model and simulation
scenarios, see \Cref{sec:app:more_maths}. The initial concentrations
in the three-dimensional domain $\Omega$ and networks $\Lambda_a,
\Lambda_v$ are all set to zero.

>>>>

\subsection*{In-silico predictions of intracranial molecular enrichment and clearance after intrathecal injection}
\begin{figure}
    \centering
    \includegraphics[width=1\textwidth]{figures/figure1.png}
     \caption{
     \textbf{Our in-silico model predicts tracer transport in PVS, SAS and parenchyma following intrathecal injection.}\\
     A) Illustration of the spatial domains of the model: CSF-filled space (ventricles and SAS) $\Omega_{\rm CSF}$, parenchyma $\Omega_{\rm PAR}$ and the PVS surrounding arteries $\Lambda_{\rm artery}$ and the veins $\Lambda_{\rm vein}$ and their interfaces and boundaries (see Methods); 
     B) 3D rendering of the actual geometry used in this study parenchyma, CSF (clipped, blue), arterial network (red), venous network (blue)); 
     C) illustration of the modelled clinical tracer injection procedure; 
     D) simulated tracer concentration after 1, 6, 12, and 24 hours (opacity increases linearly from 0 to $2\,$mol/l); 
     E) sagittal, coronal and axial view of computed tracer concentrations over T1-image after 1, 6, 12 and 24\,h (low concentrations transparent, pial surface in pink, arachnoid membrane in cyan, and arteries in dark red); 
     F) average tracer concentration in each compartment over the first 24\,h. 
     G) total amount of tracer in each cranial compartment over the first 24\,h; }
     \label{fig:results1}
\end{figure}
Using previously published multi-modal magnetic resonance imaging
(MRI) data~\cite{hodneland2019new, deistung2009tof,
  schweser2012quantitative, reichenbach2012future,
  deistung2017overview}, we construct a multiscale computational
representation of the human intracranial compartments consisting of
the CSF spaces and brain parenchyma as three-dimensional (3D) domains
and with the PVSs surrounding major surface arteries and veins as
embedded networks of topologically one-dimensional (1D) curves
(\Cref{fig:results1}A--B). We consider a solute concentration field,
varying in space and time, in the 3D domains and in the PVS networks,
and assume that the solute can cross between these compartments
through semi-permeable membranes. As the drivers and modes of
intracranial transport are under substantial
debate\cite{smith2019going, proulx2021cerebrospinal,
  bohr2022glymphatic, hladky2022glymphatic, betsholtz2024advances},
our first target is to establish a baseline model accounting for a
reasonably conservative set of mechanisms and their integrated effect
over a timescale of several minutes to a few days. To this end, we
assume that the solute will (i) diffuse within all compartments, with
diffusivity depending on the effective properties of the relevant
medium\cite{sykova2008diffusion}; (ii) experience significant
dispersive effects due to the pulsatile flow of CSF induced by the
cardiac and respiratory cycles\cite{vinje2019respiratory,
  sharp2019dispersion, ray2021quantitative, troyetsky2021dispersion};
and (iii) be convected by a (small) net flow of CSF resulting from
production in the choroid plexus with CSF efflux across the upper
convexity\cite{hornkjol2022csf} and from the peristaltic pumping
effect of pulse wave pulsations in surface periarterial
spaces~\cite{mestre2018flow, gjerde2023directional}. Mathematically, this model is represented by a
mixed-dimensional system of coupled time-dependent partial
differential equations\cite{masri2024modelling}, which we solve
numerically with high accuracy using a mass-conserving finite element
scheme and the FEniCS finite element software\cite{alnaes2015fenics,
  kuchta2020assembly} (see Methods). The computational framework and
associated software are all openly available~\cite{ZENODO}.

Simulating a glymphatic MRI protocol~\cite{ringstad2017glymphatic,
  ringstad2018brain, eide2024functional}(\Cref{fig:results1}C), we then predict the
spreading of $0.5$ mmol intrathecally injected Gadobutrol after its
appearance at the craniocervical junction
(\Cref{fig:results1}D--E). After one hour, the in-silico
tracer moves upwards in the SAS frontally of the brainstem, and
quickly reaches the supratentorial regions. Here, it spreads both
posterior through the quadrigeminal cistern and the longitudinal
fissure, and anteriorly through the outer SAS, reaching the top of the
cerebral cortex after around 12 hours. After 24 hours, the tracer
covers most of the brain surface (with the exception of some posterior
regions) and has penetrated substantially into the parenchymal
tissue. This pattern is reflected in the mean tracer concentrations in
each compartment, where the CSF space reaches its peak of
$1.4\,$mmol/l after 2 hours, followed by the arterial PVS
concentration peak ($2.9\,$mmol/l after 4 hours)
(\Cref{fig:results1}F). While the mean concentrations in these
compartments drop soon after peaking, the parenchymal tissue
slowly enriches with tracer over the first 24 hours, with a final
value of $0.3$ mmol/l. Overall, about 40\% of the total amount of
tracer remains in the cranium 24 hours post-injection, with the largest
share in the CSF (53\%), followed by the parenchyma (35\%), the
venous PVS (8\%) and the arterial PVS
(5\%) (\Cref{fig:results1}G).

@@

Our periarterial network extends from the internal carotid arteries
and basilar artery through up to 18 bifurcations to reach upstream
network ends located within the SAS or up to 6 mm inside the
parenchyma (\Cref{fig:results1}A--B, \Cref{fig:pvs_a}A) and includes
major surface arteries of radius 0.5--1.4 mm. Imposing the pressure
field induced by CSF production at the periarterial network ends
induces slow steady CSF flow of variable direction in these PVSs, with
an average velocity of 0.08 \textmu m/s (antegrade) and a maximum
velocity of 0.55 \textmu m/s (\Cref{fig:pvs_a}B). On the other hand,
traveling waves of arterial wall motion (\Cref{fig:pvs_a}C), such as
the pulse wave or other vasomotion~\cite{vanveluw2020vasomotion,
  munting2023spontaneous, bojarskaite2023sleep,
  broggini2024long,hauglund2025norepinephrine}, also induce net
directional flow in the PVS~\cite{kedarasetti2020arterial,
  kedarasetti2020functional, coenen2021lubrication,
  gjerde2023directional, nozaleda2024arterial} -- of magnitude and
direction depending on the amplitude, frequency, and length of the
waves and the characteristics of the perivascular
network~\cite{gjerde2023directional}. Applying a semi-analytic model
of the net flow induced by peristalsis in perivascular
networks~\cite{gjerde2023directional} (see Methods), we estimate that
the cardiac pulse wave alone, travelling at a frequency of 1 Hz with a
wavelength of 2.0 m and a 1\% wall displacement~\cite{jung2021novel},
will induce mainly antegrade PVS flow with an average net velocity of
0.92 \textmu m/s while reaching up to 7.31 \textmu m/s near larger,
ventral vessels such as the MCA (\Cref{fig:pvs_a}D,E). The same theory
predicts that strong ultraslow vasomotions, if travelling antegrade at
0.1Hz with a wavelength of 0.02 m and a 10\%
displacement~\cite{broggini2024long}, will induce both retrograde and
antegrade net PVS flow with an average velocity of 13.05 \textmu m/s
and maximum velocity 54.44 \textmu m/s (\Cref{fig:pvs_a}D,F).

@@

To represent surface networks of periarterial and perivenous spaces,
we use Kiminaro~\cite{william_silversmith_2021_5539913} to separately
skeletonize time-of-flight angiography (ToF) and quantitative
susceptibility mapping (QSM) images from the same human
subject~\cite{hodneland2019new}. This technique yields networks of
one-dimensional curves, each curve $\Lambda^i$ indicating the
centerline of a blood vessel segment and labeled with its lumen radius
$R_1^i$ (\Cref{fig:pvs_a}A). We also assign an
outer radius $R_2^i > R_1^i$ to each segment $i$, form the annular
cylinder ensheathing $\Lambda^i$ and define the union of these as the
PVS. The periarterial network graph consists of $12\,708$ edges
connected at $12\,562$ inner nodes and with $147$ end nodes, and the
associated domain is denoted by $\Lambda_a$. We identify three of the
end nodes -- corresponding to the two internal carotid arteries (ICAs)
and the basilar artery (BA) -- as root nodes, and designate the other
ends as leaf nodes. The resulting perivenous network graph consists of
$24\,829$ edges connected at $23\,881$ inner nodes and with $949$ end nodes, and the associated domain is denoted by $\Lambda_v$. Finally, we label the outer surface of the PVSs associated with $\Lambda_a$ and $\Lambda_v$, by $\Gamma_a$ and $\Gamma_v$ respectively.

@@

We model diffusion, convection, and exchange of a molecular solute in
the PVS networks $\Lambda_a$ and $\Lambda_v$, in the CSF spaces
$\Omega_{\rm CSF}$ and in the brain parenchyma $\Omega_{\rm PAR}$ via
a mixed-dimensional transport model~\cite{masri2024modelling,laurino2019derivation} over a
timescale of minutes to hours (\Cref{fig:results1}A--B,
\Cref{fig:csf}A--C). Specifically, for $t > 0$, we solve for a
concentration $c = c(x, t)$ in the 3D intracranial compartments ($x
\in \Omega_{\rm CSF}, x \in \Omega_{\rm PAR}$) and for a cross-section
averaged concentration $\hat{c} = \hat{c}(s, t)$ in the periarterial
and perivenous networks ($s \in \Lambda_a, s \in \Lambda_v$) such that
the following equations hold:
\begin{subequations}
\begin{alignat}{2}
  \partial_t (\phi c) - \nabla \cdot (D \nabla (\phi c) ) + \nabla \cdot (\bm u c ) + \xi (\overline{c} - \hat c ) \delta_\Gamma & = 0 && \quad \quad \mathrm{in} \quad \Omega_{\rm CSF}, \Omega_{\rm{PAR}},
  \label{eq:multi_transport_3d}
  \\ 
  \partial_t (A  \hat c) - \partial_s(\hat D A \partial_s ( \hat c)) +\partial_s(A \hat u \hat c )  +  \xi P (\hat c - \overline{c})  &= 0 && \quad \quad \mathrm{in} \quad  \Lambda_a, \Lambda_v .
  \label{eq:multi_transport_1d}
 \end{alignat}%
\label{eq:multi_transport}%
\end{subequations}%
In~\eqref{eq:multi_transport}, $0 < \phi \leqslant 1$ is the fluid
volume fraction, $D$ and $\hat{D}$ are effective diffusion
coefficients, and $\bm u$ and $\hat{u}$ are fluid (CSF/ISF)
velocities, all defined in the respective compartments; $P = 2 \pi
R_2$ is the perimeter and $A = \pi (R_2^2 - R_1^2)$ the area of the
PVS cross-sections, $\delta_{\Gamma}$ is a Dirac term concentrated on
the interfaces $\Gamma_a, \Gamma_v$, the overlined $\overline{c}$
denotes the average of $c$ over cross-sections of $\Gamma_a,
\Gamma_v$, and $\xi$ is a permeability allowing for transfer/exchange
over the interfaces $\Gamma_a, \Gamma_v$ between the periarterial and
perivenous networks and their surroundings.  Moreover, we model the
membrane between the parenchyma and the CSF spaces as a semi-permeable
membrane with permeability coefficient $\beta_{\rm pia}$. For a
complete description of this mathematical model and simulation
scenarios, see \Cref{sec:app:more_maths}. The initial concentrations
in the three-dimensional domain $\Omega$ and networks $\Lambda_a,
\Lambda_v$ are all set to zero.

### 2025-02-25 paper/supplementary_main.tex
update Fig1 caption and references

This theoretical formalism~\cite{gjerde2023directional} is defined
relative to a network in the form of a directed, bifurcating tree with
a single supply node/root $i_0$. To extend to a network of cerebral
arteries with multiple supply nodes (such as the basilar and two
internal carotid arteries in the current data
set~\cite{hodneland2019new}), we separate the network $\Lambda$ into
edge-disjoint subnetworks $\Lambda^1, \Lambda^2, \Lambda^3$, one for
each of the supply nodes (\Cref{fig:results1}A, C,
\Cref{fig:app:peristalsis}). Each node is assigned to the subnetwork
associated with the nearest supply node, and edges between nodes are
preserved (\Cref{fig:app:peristalsis}B). Next, we compute a minimal,
bifurcating and directed tree representation of each subnetwork:
$\mathcal{T}^1, \mathcal{T}^2, \mathcal{T}^3$
(\Cref{fig:app:peristalsis}C). Each tree $\mathcal{T}^j = \cup E_n^j$
consists of the subset of the nodes from $\Lambda^j$ that have degree
1 (are leaf or root nodes) or degree $3$ (are true bifurcation
points), and each path between nodes with degree $\not = 2$ in
$\Lambda^j$ is represented in $\mathcal{T}^j$ by an edge $E^j$ with
edge length $L$ corresponding to the total length of the original path
and edge radius $R^j$ as the average of the path radii.

>>>>

This theoretical formalism~\cite{gjerde2023directional} is defined
relative to a network in the form of a directed, bifurcating tree with
a single supply node/root $i_0$. To extend to a network of cerebral
arteries with multiple supply nodes (such as the basilar and two
internal carotid arteries in the current data
set~\cite{hodneland2019new}), we separate the network $\Lambda$ into
edge-disjoint subnetworks $\Lambda^1, \Lambda^2, \Lambda^3$, one for
each of the supply nodes (\Cref{fig:results1}A--B,
\Cref{fig:app:peristalsis}). Each node is assigned to the subnetwork
associated with the nearest supply node, and edges between nodes are
preserved (\Cref{fig:app:peristalsis}B). Next, we compute a minimal,
bifurcating and directed tree representation of each subnetwork:
$\mathcal{T}^1, \mathcal{T}^2, \mathcal{T}^3$
(\Cref{fig:app:peristalsis}C). Each tree $\mathcal{T}^j = \cup E_n^j$
consists of the subset of the nodes from $\Lambda^j$ that have degree
1 (are leaf or root nodes) or degree $3$ (are true bifurcation
points), and each path between nodes with degree $\not = 2$ in
$\Lambda^j$ is represented in $\mathcal{T}^j$ by an edge $E^j$ with
edge length $L$ corresponding to the total length of the original path
and edge radius $R^j$ as the average of the path radii.
